Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-10-15 icde2016/intro.tex
corpi -> corpora

Specifically, our contributions include:
\begin{itemize}
\item By analyzing an online corpus, we provide evidence that practical date parsing requires the ability to recognize hundreds of formats;
\item We show how to extend prior work on Minimum Descriptive Length structure extraction to generate a freely available date format domain language with over 95\% accuracy;
\item We describe a second Natural Language Processing technique for generating the same date format domain language with similar accuracy. We describe how the basic algorithm is extended to support grammar variants and constraints unique to date formats. The parsing algorithm is extended to compute an overall dominant pattern over a data column;
\item We provide evidence that the development of multiple, independent parsing algorithms provides an effective means of cross-validation on large corpi;
\item We describe some limitations of this domain language that would improve its utility.
\end{itemize}

>>>>

Specifically, our contributions include:
\begin{itemize}
\item By analyzing an online corpus, we provide evidence that practical date parsing requires the ability to recognize hundreds of formats;
\item We show how to extend prior work on Minimum Descriptive Length structure extraction to generate a freely available date format domain language with over 95\% accuracy;
\item We describe a second Natural Language Processing technique for generating the same date format domain language with similar accuracy. We describe how the basic algorithm is extended to support grammar variants and constraints unique to date formats. The parsing algorithm is extended to compute an overall dominant pattern over a data column;
\item We provide evidence that the development of multiple, independent parsing algorithms provides an effective means of cross-validation on large corpora;
\item We describe some limitations of this domain language that would improve its utility.
\end{itemize}
